Verifying Demonstrations

### 2017-08-27 fig/tposet.tex
Fixes arrows in poset graph
The arrows should be the other direction, since it links backwards, not
forwards.

  \path
  (prev) edge node [right] {} (ts)
  (ts) edge node {} (pA)
  (pA) edge node {} (te)
  (ts) edge node {} (pB)
  (pB) edge node {} (te)
  (te) edge node {} (succ);

>>>>

  \path
  (succ) edge node {} (te)
  (te) edge node {} (pB)
  (pB) edge node {} (ts)
  (te) edge node {} (pA)
  (pA) edge node {} (ts)
  (ts) edge node {} (prev);
